Networked Character Devices

### 2011-12-08 report/presentation.tex
presentation: typo s/Server/Client/
Added system images

\title[NCD]{Networked Character Devices}
%\subtitle[]{}
\author[Monaco, Sayler, Spear]{Matthew Monaco \&
                               Andy Sayler \&
                               Landon Spear}
\institute[CU-Boulder]{
  University of Colorado at Boulder \\
  \texttt{\{first.last\}@colorado.edu}
}
\date[Dec. 10, 2011]{Saturday, December 10\textsuperscript{th}, 2011}

@@

\section{Results and Evaluation}
%---Current State Slide---%
\begin{frame}{\bf Current State}

\begin{packed_item}
\item Supports exporting a single character device from the server
\item Supports importing a single character device on the client
\item Supports open, close, read, and write calls
\item Supports basic Linux udev operation for automatic node creation on client
\end{packed_item}

@@

\begin{packed_item}
\item Multi-device, multi-server client-side import support
\item Multi-device server-side export support
\item Support for exclusive use and protection of exported devices
\item Support for ioctl calls
\item Support for providing and obtaining metadata for exported
  devices
\item Support for ``advertisement'' of available exported devices
\item Support for integrating imported devices into other kernel
  subsystems (human interface subsystem, audio subsystem, etc)
\item Addition of ``NCD-admin'' utilities for managing and administering
  NCD system
\end{packed_item}

>>>>

\title[NCD]{Networked Character Devices}
%\subtitle[]{}
\author[Monaco, Sayler, Spear]{Matthew Monaco \&
                               Andrew Sayler \&
                               Landon Spear}
\institute[CU-Boulder]{
  University of Colorado at Boulder \\
  \texttt{\{first.last\}@colorado.edu}
}
\date[Dec. 10, 2011]{Saturday, December 10\textsuperscript{th}, 2011}

@@

\section{Results and Evaluation}
%---Full State Slide---%

\begin{frame}[c]{Full System}
  \begin{center}
    \includegraphics[height=0.75\paperheight,keepaspectratio]{system-full.png}
  \end{center}
\end{frame}

%---Current State Image Slide---%
\begin{frame}[c]{Current State}
  \begin{center}
    \includegraphics[height=0.75\paperheight,keepaspectratio]{system-working.png}
  \end{center}
\end{frame}

%---Current State Slide---%
\begin{frame}{\bf Current State}

\begin{itemize}
\item<1-> Supports exporting a single character device from the server
\item<2-> Supports importing a single character device on the client
\item<3-> Supports open, close, read, and write calls
\item<4-> Supports basic Linux udev operation for automatic node creation on client
\end{itemize}

@@

\begin{itemize}
\item Multi-device, multi-server client-side import support
\item Multi-device server-side export support
\item Support for exclusive use and protection of exported devices
\item Support for ioctl calls
\item Support for providing and obtaining metadata for exported
  devices
\item Support for ``advertisement'' of available exported devices
\item Support for integrating imported devices into other kernel
  subsystems (human interface subsystem, audio subsystem, etc)
\item Addition of ``NCD-admin'' utilities for managing and administering
  NCD system
\end{itemize}
